Introduction to Markov state modeling with the PyEMMA software --- v\versionnumber

### 2018-08-27 manuscript/manuscript.tex
minor caption changes (#137)

\begin{figure}
\includegraphics{figure_2}
\caption{Exemplary analysis of the conformational dynamics of a pentapeptide backbone: (a)~The Trp-Leu-Ala-Leu-Leu pentapeptide in licorice representation~\cite{vmd}.
(b)~The VAMP-2 score indicates which of the tested featurizations contains the highest kinetic variance.
(c)~The sample density projected onto the first two time-lagged independent components (ICs) at lag time $\tau=0.5$ ns shows multiple density maxima and
(d)~the time series of the first two ICs show rare transition events.
(e)~The convergence behavior of the first four implied timescales indicates that a lag time of $\tau=0.5$ ns is suitable for MSM estimation.
(f) A Chapman-Kolmogorov test shows that an MSM estimated at lag time $\tau=0.5$ ns under the assumption of five metastable states accurately predicts the kinetic behavior on longer timescales.
In~(e) and~(f), the shaded areas indicate $95\%$ confidence intervals computed with a Bayesian sampling procedure.}
\label{fig:io-to-ck}
\end{figure}

@@

\begin{figure}
\includegraphics{figure_3}
\caption{Exemplary analysis of the conformational dynamics of a pentapeptide backbone:
(a) The reweighted free energy surface projected onto the first two independent components exhibits five minima which
(b) PCCA++ identifies as five metastable states.
(c) The second right eigenvector shows that the slowest process shifts probability between the least probable state ($\mathcal{S}_1$) and the other states, in particular states ($\mathcal{S}_4$, $\mathcal{S}_5$), whereas
(d) the committor $\mathcal{S}_2\to\mathcal{S}_4$ indicates that states $\mathcal{S}_{(1,3,5)}$ act as a transition region between states $\mathcal{S}_2$ and $\mathcal{S}_4$.}
\label{fig:msm-analysis}
\end{figure}

@@

\begin{figure}
\includegraphics{figure_4}
\caption{Visualization of the transition paths from $\mathcal{S}_2$ to $\mathcal{S}_4$:
Metastable states $\mathcal{S}_{(1-5)}$ are represented by an ensemble of representative structures and are arranged along the horizonal axis according to their committor probabilities. The three main transition pathways starting from $\mathcal{S}_2$ and ending in $\mathcal{S}_4$ are depicted by gray arrows with thickness proportional to the transition flux. The dominant pathway proceeds through $\mathcal{S}_5$.}
\label{fig:tpt-network}
\end{figure}

@@

\begin{figure}
\includegraphics{figure_5}
\caption{The Trp-1 SASA autocorrelation function yields a weak signal (a) which, however, can be enhanced if the system is prepared in the nonequilibrium condition $\mathcal{S}_1$ (b). The solid/orange lines denote the maximum likelihood MSM result; the dashed/blue lines and the the shaded areas indicate sample means and $95\%$ confidence intervals computed with a Bayesian sampling procedure.}
\label{fig:msm-exp-obs}
\end{figure}

>>>>

\begin{figure}
\includegraphics{figure_2}
\caption{Example analysis of the conformational dynamics of a pentapeptide backbone: (a)~The Trp-Leu-Ala-Leu-Leu pentapeptide in licorice representation~\cite{vmd}.
(b)~The VAMP-2 score indicates which of the tested featurizations contains the highest kinetic variance.
(c)~The sample density projected onto the first two time-lagged independent components (ICs) at lag time $\tau=0.5$ ns shows multiple density maxima and
(d)~the time series of the first two ICs show rare transition events.
(e)~The convergence behavior of the first four implied timescales indicates that a lag time of $\tau=0.5$ ns is suitable for MSM estimation.
(f) A Chapman-Kolmogorov test shows that an MSM estimated at lag time $\tau=0.5$ ns under the assumption of five metastable states accurately predicts the kinetic behavior on longer timescales.
In~(e) and~(f), the shaded areas indicate $95\%$ confidence intervals computed with a Bayesian sampling procedure.}
\label{fig:io-to-ck}
\end{figure}

@@

\begin{figure}
\includegraphics{figure_3}
\caption{Example analysis of the conformational dynamics of a pentapeptide backbone:
(a)~The reweighted free energy surface projected onto the first two independent components exhibits five minima which
(b)~PCCA++ identifies as five metastable states.
(c)~The second right eigenvector shows that the slowest process shifts probability between the least probable state ($\mathcal{S}_1$) and the other states, in particular states ($\mathcal{S}_4$, $\mathcal{S}_5$), whereas
(d)~the committor $\mathcal{S}_2\to\mathcal{S}_4$ indicates that states $\mathcal{S}_{(1,3,5)}$ act as a transition region between states $\mathcal{S}_2$ and $\mathcal{S}_4$.}
\label{fig:msm-analysis}
\end{figure}

@@

\begin{figure}
\includegraphics{figure_4}
\caption{Example analysis of the conformational dynamics of a pentapeptide backbone:
visualization of the transition paths from $\mathcal{S}_2$ to $\mathcal{S}_4$.
Metastable states $\mathcal{S}_{(1-5)}$ are represented by an ensemble of representative structures and are arranged along the horizonal axis according to their committor probabilities. The three main transition pathways starting from $\mathcal{S}_2$ and ending in $\mathcal{S}_4$ are depicted by gray arrows with thickness proportional to the transition flux. The dominant pathway proceeds through $\mathcal{S}_5$.}
\label{fig:tpt-network}
\end{figure}

@@

\begin{figure}
\includegraphics{figure_5}
\caption{Example analysis of the conformational dynamics of a pentapeptide backbone: the Trp-1 SASA autocorrelation function yields a weak signal (a) which, however, can be enhanced if the system is prepared in the nonequilibrium condition $\mathcal{S}_1$ (b). The solid/orange lines denote the maximum likelihood MSM result; the dashed/blue lines and the the shaded areas indicate sample means and $95\%$ confidence intervals computed with a Bayesian sampling procedure.}
\label{fig:msm-exp-obs}
\end{figure}
